Deep and Shallow Types for Gradual Languages

### 2022-05-23 g-pldi-2022/camera-tex/paper.tex
pldi: affiliation++

\keywords{gradual typing, migratory typing, complete monitoring, type{-}enforcement strategies}
\title{Deep and Shallow Types for Gradual Languages}
\author{Ben Greenman}{\orcid{0000{-}0001{-}7078{-}9287}}{\affiliation{\institution{Brown University}\country{USA}}}{\email{benjamin.l.greenman@gmail.com}}
\maketitle
\label{t:x28part_x22Deepx5fandx5fShallowx5fTypesx5fforx5fGradualx5fLanguagesx22x29}

\noindent

\noindent

\Ssection{A Spectrum of Type Enforcement}{A Spectrum of Type Enforcement}\label{t:x28part_x22secx3aintroductionx22x29}

>>>>

\keywords{gradual typing, migratory typing, complete monitoring, type{-}enforcement strategies}
\title{Deep and Shallow Types for Gradual Languages}
\author{Ben Greenman}\authornote{Research done at Northeastern University}{\orcid{0000{-}0001{-}7078{-}9287}}{\affiliation{\institution{Brown University}\country{USA}}}{\email{benjamin.l.greenman@gmail.com}}
\maketitle
\label{t:x28part_x22Deepx5fandx5fShallowx5fTypesx5fforx5fGradualx5fLanguagesx22x29}

\sectionNewpage
\vspace{-0.5em}
\Ssection{A Spectrum of Type Enforcement}{A Spectrum of Type Enforcement}\label{t:x28part_x22secx3aintroductionx22x29}
